Correlation between different emission channels from an atom inside a leaky driven cavity\\ \thanks{corresponding author e-mail: guillermopreisser@hotmail.com}

### 2019-11-09 paper1.2.1.tex
Add files via upload
Commit intermedio, muchos cambios hechos por pablo

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{amsfonts,amsmath, amssymb}
%\usepackage[spanish]{babel}
\usepackage{fancyhdr}
%\usepackage[none]{hyphenat}
\usepackage[nottoc, notlot, notlof]{tocbibind}
\usepackage{cite}
\usepackage{physics}
\usepackage{bm}
\usepackage{enumitem}
\usepackage{a4wide}
\usepackage{dsfont}
\usepackage{ amssymb }
\usepackage{cite}
\usepackage[rightcaption]{sidecap}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{ragged2e}
\usepackage{pdfpages} 
\usepackage{csquotes}
\usepackage{listings}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=blue,      
    urlcolor=blue,
    citecolor=blue,
}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Correlation between atom and cavity emissions in a driven Jaynes-Cummings system\\
%{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
%should not be used}
\thanks{corresponding author e-mail: guillermopreisser@hotmail.com}
}

@@

\begin{abstract}
We consider a driven Jaynes-Cummings system under weak coupling, which interacts with the environment through emissions from the atom and emissions that leak through one of the lateral cavity mirrors.  We fix the parameters of the model in order to stablish a dynamic in which the number of photons in the leaky cavity remain constant and, using quantum trajectory theory, we estimate the number of spontaneous emissions in the two-level atom – which will be measured from the upper side of the cavity – by measuring emissions that leak through one of the semi-transparent cavity mirrors. Studying the system further we find that the cavity generates a correlation between the emissions from the two sources.
\end{abstract}

%the recent advances?
\section{Introduction}
Spontaneous emission is a phenomenon that has been studied formally since early XX century \cite{10.2307/94746, 1917PhyZ...18..121E}. One of the main characteristics of spontaneous emission is that, while it is known that an atom will decay exponentially, the exact time of emission, as well as the direction in  which the photon is emitted, is random, which difficults its measurement. On the other hand, photons emitted from a stimulated cavity are easy to measure, partly due the fact that we know that they leave the cavity through one of the lateral mirrors \cite{326305, doi:10.1063/1.113345}. One of the main sources for single photons are two-level atoms. However, due to the randomness of the direction in which the photons are emitted, there are difficulties in managing such sources. To sort out this difficulty one could think of a physical arrangement, in which the two-level atom is coupled to the stimulated mode of a cavity, as it is shown in Fig. \ref{asa} (b). In this physical arrangement, which is known as the driven Jaynes-Cummings model, one could try to estimate the number of spontaneous emissions of the atom, which are emitted in the upper and lower directions of the system, by measuring the photons that leak through one of the cavity mirrors, on the lateral side. In the case that a correlation exists between the two quantities, this could turn useful in the manipulation of two-level atoms as single photon sources. 
\begin{center}
\begin{figure*}\label{asa}
\begin{center}
\includegraphics[scale = 0.65]{newimagepaper.pdf}
%\includegraphics[scale = 0.45]{image_paper222.png}
\caption{\small{Physical arrangements of atom and atom in a cavity. In both of these arrangements we consider a source which stimulates the atom provoking it to spontaneously emit, once it decays. We consider a detector in two directions, and we keep a register of the number of photons measured in each direction. (a) In the case for the atom we don't expect a correlation between m (the number of photons measured in the upper side of the atom) and n (the number of photons measured in the right side of the atom); (b) for the atom in the cavity (a cavity with some loss rate) we study the possibility that the cavity generates a correlation between the emissions of the atom and the emissions of the cavity, which correspond to the emissions that leak through mirror 2.}} \label{probdisult}
\end{center}
\end{figure*}
\end{center}

It is easy to see why there would be no correlation between the directions of the emissions in the case for the two-level atom, without cavity. At the moment of modelling such physical system we consider a Markovian dynamic (i.e., the environment relaxes rapidly to an equilibrium state and on relevant timescales has no memory of previous interactions with the system \cite{daley2014quantum}). Given that the only way for a correlation to happen between the two emissions would be if one the emissions stay registered in the environment and, somehow, later influence the quantum system at a later time; by taking account of the Markovian dynamic we can have certainty that there is no direct correlation between the number of emissions of each source. Nevertheless, for the case of the atom coupled to a mode of a cavity, before a photon is emitted, it will most likely interact with the atom for some time. We consider the possibility that this interaction with the atom before the emission could contribute to the generation of a correlation between the emissions, which is what we study further in this paper.

In order to simulate quantum systems with dissipation and loss of coherence, like the one we deal with in this work, we use quantum trajectory theory. %Quantum trajectory was developed for various groups at the beginning of the 90's
One can define a quantum trajectory as the description of a continuously monitored quantum system conditioned on a particular past history of coherent evolution and collapse \cite{Carmichael1993Open}. These trajectories are simulated through a stochastic process, which define the times when the collapses occur.

In this work we estimate the number of spontaneous emissions by measuring stimulated emissions in an optical cavity and we calculate the existing correlation between the two emissions. This is done via quantum trajectories in which, by doing a large number of simulation and making a register of the number of spontaneous emissions and cavity emissions, we obtain probability distributions which relates these two quantities. We proceed in doing numerical calculations in order to prove that there is a correlation between two quantities, and we see how this correlation varies with respect to the cavity linewidth. \\

This article is set up as follows: A general overview of the driven Jaynes-Cummings model is presented in section two. In section three we obtain probability distributions that relate the number of spontaneous and cavity emissions. In section four we calculate the correlation between the two variables. Concluding remarks are given in section six.

\section{Driven Jaynes-Cummings model}
We consider a system consisting of a two-level atom, coupled to a mode of a cavity. The mode is driven by a coherent field resonant with the atom and the mode of the cavity. In order to account for dissipation one may use a non-hermitian Hamiltonian to describe the system \cite{bla}. Using this description for the system will turn useful at the moment of using quantum trajectory theory. Such Hamiltonian can be separated into hermitian and non-hermitian terms.
%\begin{equation}
%H = H_s - \frac{i\hbar}{2}\sum_m C^\dagger_n C_n .
%\end{equation}
The hermitian part of our Hamiltonian is given by $H_s$ which for the driven Jaynes-Cumming, under the rotating wave approximation, reads as
\begin{equation}
H_s = H_{at} + H_{cav} + H_{atcav} + H_{lascav}, \label{mainham}  
\end{equation}
where the atom and cavity terms are, respectively
\begin{subequations}
\begin{equation}
H_{at} = \tfrac{1}{2}\hbar \omega \sigma_z,    
\end{equation}
\begin{equation}
H_{cav} = \hbar \omega  a^\dagger a,  
\end{equation}
while the coupling between atom and cavity, and cavity and coherent field are
\begin{equation}
H_{atcav} = i\hbar g(a\sigma_+ - a^\dagger \sigma_-),    
\end{equation}
\begin{equation}
H_{lascav} = i\hbar \mathcal{E}(ae^{i\omega t} - a^\dagger e^{-i\omega t}),    
\end{equation}
\end{subequations}
where we introduced the coupling constant
\begin{equation}
g = \sqrt{\frac{\omega d^2}{2\hbar \epsilon_0 V_Q}},
\end{equation}
with the mode volume $V_Q$, dipolar coupling constant $d$, and $\epsilon_0$ is the permitivity of free space. $\mathcal{E}$ is a term proportional to the coherent field amplitude.
As for the non-hermitian part of our Hamiltonian, we have
\begin{equation} \label{nh}
H_{nh} = H_{dec} + H_{leak},
\end{equation}
where the terms corresponding to the spontaneous emission of the atom and the cavitty losses are
\begin{subequations}
\begin{equation}
H_{dec} = - i\hbar\frac{\gamma}{2}\sigma_+\sigma_-,
\end{equation}
\begin{equation}
H_{leak} = - i\hbar\kappa a^\dagger a.
\end{equation}
\end{subequations}
The annihilation operator $a$ of a single photon in the cavity, and the creation operator $a^\dagger$ obey $[a, a^\dagger] = 1$. The operators $\sigma_-, \sigma_+$  account for the atomic lowering and raising operators, respectively, and the operator $\sigma_z$ accounts for the population difference between the atomic levels. These operators obey $[\sigma_+, \sigma_-] = \sigma_z, \ [\sigma_\pm, \sigma_z] = \mp 2\sigma_\pm$. $\kappa$ and $\gamma$ are the cavity loss and spontaneous decay rate.\\

\section{Estimation of spontaneous emissions}
In this section we obtain estimations for the number of spontaneous emissions by measuring stimulated emission in a cavity mode in the driven Jaynes-Cummings model, using quantum trajectory theory.
\subsection{Probability distributions of emissions}
In order to get the desired estimations, first we must obtain probability distributions that relate the number of spontaneous emissions of the atom with the emissions measured from the cavity. We achieve this by making a large number of quantum  trajectories from which we keep a record of the number of spontaneous emissions and cavity losses, relating the number of spontaneous emissions for each number of cavity loss and making a probability distribution out of the emission's register of the trajectories.

In order to achieve this, following the procedure from quantum trajectory theory as it is explained in \cite{bla}. Starting with a state which represents a ground state of the atom with no photons in the cavity, $\ket{\phi(t = 0)} = \ket{\downarrow} \times \ket{0}$, we evolve it with the Schrödinger equation through some time $\delta t$, using a non-hermitian Hamiltonian of the form
\begin{equation}
H = H_s - \frac{i\hbar}{2}\sum_n C^\dagger_n C_n,
\end{equation}
where the operators $C_n$ are known as collapse operators.
Using a non-hermitian Hamiltonian will have as a consequence that the probability won't be conserved \cite{Sakurai:1167961}. The evolution of the state through the schrödinger equation will be interrupted by a quantum jump – an abrupt change on our state in which a photoemission has ocurred. The probability for such quantum jump to happen will be given by the collapse probability
\begin{equation} \label{probcol}
\delta p = \sum_n \delta p_n,
\end{equation}
where 
\begin{equation} \label{relprob}
\delta p_n = \delta t \bra{\phi (t)} C^\dagger_n C_n \ket{\psi (t)}.
\end{equation}
We use these collapse probabilities to simulate the quantum trajectories, where we compare the collapse probability of eq. \eqref{probcol} with a random number $\epsilon$, uniformly distributed between zero and one. In the case the condition $\delta p > \epsilon$ is fulfilled we simulate that a quantum jump has happened, by acting with one of the collapse operators. The operator with which we'll act on the state will be given according to the relative probabilities of eq. \eqref{relprob}. From the non-hermitian Hamiltonian of our system \eqref{nh} we are able to identify the corresponding collapse operators which are
\begin{figure}[!t] 
\centering
\includegraphics[scale = 0.5]{distributioneng.pdf}
\caption{\small{Probability distribution of spontaneous emissions for different number of cavity losses in a driven Jaynes-cummings model, doing $100,000$ quantum trajectory simulations, with parameters $\mathcal{E}  = \kappa = \gamma = g = 1$.}} \label{probdiss}
\end{figure}
\begin{subequations}
\begin{equation}
C_1 = \sqrt{\gamma}\sigma_-,
\end{equation}
\begin{equation}
C_2 = \sqrt{2\kappa}a.
\end{equation}
\end{subequations}
Using equation \eqref{probcol} one can easily identify the corresponding collapse probabilities of the system. Having identified the collapse operators and the collapse probability, we simulate quantum trajectories, in which we keep count of the number of quantum jumps for each collapse operator, relating the number of quantum jumps associated to spontaneous emissions for each number of quantum jumps associated to cavity emissions until we reach a maximum number of cavity emissions, which we establish. The procedure of register of emissions is summarized in algorithm \ref{alg1}.

@@

@@

\section{Correlation between atom and cavity emissions}
So far we have obtained estimations for the number of spontaneous emission for each measured number of cavity emissions. From our results it is obvious how the number of spontaneous emissions will increase with respect to the number of cavity emissions, given that more time will pass and more emissions will occur. One can also see how increasing the cavity linewidth $\kappa$ and keeping the other parameters constant will translate into a decrease of spontaneous emissions with respect to the number of cavity emissions. However, one question remains: is there a direct correlation between these two quantities? If yes, how this varies with respect to the cavity linewidth. From the beginning one could expect that in the case for a big $\kappa$ there would be no correlation at all, since this situation will be equivalent to the situation where there is no cavity.

@@

\begin{center}
\begin{figure}[t!]
\begin{center}
\includegraphics[scale = 0.45]{cor2.pdf}
\caption{\small{Calculation of correlation using 500 time intervals, fixing $\expval{n} \approx 1$, $\gamma =$ 1.0, $g = $ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}} \label{corrxy}
\end{center}  
\end{figure}
\end{center}

\begin{center}
\begin{figure}[h!]
\begin{center}
\includegraphics[scale = 0.45]{difftimes12.pdf}
\caption{\small{Correlation using different temporal intervals, fixing $\expval{n} \approx 1$, $\gamma =$ 1.0, $g =$ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}}  \label{errorzz}
\end{center}
\end{figure}
\end{center}
%kncrease or increases
From Fig. \ref{corrxy} we see that, as we expected, the correlation goes to zero as we increase the cavity linewidth. Nonetheless, perhaps a more interesting question is: how high can this correlation be? Trying with values for $\kappa/\gamma$ lower than $0.1$, we notice that the correlation's increase stops and a decrease begins. It is possible that this stop in the increase of the correlation is due to the fact that if we keep decreasing the cavity linewidth it will come a point where the number of emissions will decrease considerably, diminishing the correlation. If this is the case we should expect that as we increase the temporal intervals, %the cavity linewidth at which the correlation starts decreasing should be smaller.
we also see an increment of the correlation.

@@

\section{Conclusions}
In this work we considered a driven Jaynes-Cummings system. We made a program in which, through the use of quantum trajectory theory, we were able to obtain probability distributions that relate the number of spontaneous emissions given certain number of cavity emissions. Through the probability distributions we obtained estimations for the number of spontaneous emissions by measuring cavity emissions, considering the correspondent error. Finally we study the existing correlation where we saw how this correlation decreases as we increase the cavity linewidth. However, if we try with values for  $\kappa/\gamma < 0.1$, there comes a point where the increase stops and we see a decrease. We believe this is related to the fact that if we use enough small values of $\kappa$ there will come a point where the emission of photons will be too low and this will imply a decrease in the correlation. The results in this work provide a tool that could be useful in the manipulation of single photons product of spontaneous emission, and provide insight into the physical behavior of the driven Jaynes-Cummings model.

@@

Support by UNAM, projects CONACyT and UNAMPAPIIT IG100518.

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{amsfonts,amsmath, amssymb}
%\usepackage[spanish]{babel}
\usepackage{fancyhdr}
%\usepackage[none]{hyphenat}
\usepackage[nottoc, notlot, notlof]{tocbibind}
\usepackage{cite}
\usepackage{physics}
\usepackage{bm}
\usepackage[draft,inline,nomargin]{fixme} \fxsetup{theme=color}
\usepackage{enumitem}
\usepackage{a4wide}
\usepackage{dsfont}
\usepackage{ amssymb }
\usepackage{cite}
\usepackage[rightcaption]{sidecap}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{ragged2e}
\usepackage{pdfpages} 
\usepackage{csquotes}
\usepackage{listings}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=blue,      
    urlcolor=blue,
    citecolor=blue,
}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Correlation between different emission channels from an atom inside a leaky driven cavity\\
%{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
%should not be used}
\thanks{corresponding author e-mail: guillermopreisser@hotmail.com}
}

@@

\begin{abstract}
  A two level atom in free space does not show any correlation between
  photons emitted in different directions. We consider a two level
  atom inside a driven leaky cavity. We consider two atomic emission
  channels: emission to cavity modes and emission to no-cavity modes.
  Using the quantum trajectory formalism we study the correlation
  between photons emitted into cavity modes and that leak the cavity
  through its mirror, with photons that are emitted into the rest of
  the modes. We find that the cavity generates a correlation between
  the two emission channels.
\end{abstract}

%the recent advances?
\section{Introduction}
Spontaneous emission is a phenomenon that has been studied since the
early XX century \cite{10.2307/94746, 1917PhyZ...18..121E}. One of the
main characteristics of spontaneous emission is that
\fxnote{spontaneus emission no es exponencial, es aproximadamente
  exponencial, si quitas la aproximacion markoviana te queda una cola
  polinomial, quite la oracion} the exact time of emission, as well as
the direction in which the photon is emitted, is random, which
difficults its measurement. On the other hand, photons emitted from a
cavity are easy to measure, partly due the fact that we know that they
leave the cavity through one of the lateral mirrors \cite{326305,
  doi:10.1063/1.113345}. The randomness of the direction in which the
photons are emitted by atoms in free space difficults photon counting
experiments. To sort out this difficulty one could think of a physical
arrangement, in which the two-level atom is coupled to the stimulated
mode of a cavity, as it is shown in Fig. \ref{asa} (b). In this
physical arrangement, \fxnote*{tienes una cita donde lo nombren
  asi?}{which is known as the driven Jaynes-Cummings model}, one could
try to estimate the number of spontaneous emissions of the atom
--which are emitted in modes that are not cavity modes and therefore
escape the cavity-- by measuring the photons that leak through one of
the cavity mirrors. In the case that a
correlation exists between the two quantities, we can count the number
of photons that leak the cavity through its mirror, which is easy to
measure, to find information about the number of photons emitted into
the other modes (spontaneus emission), which are difficult to measure.
\begin{center}
\begin{figure*}\label{asa}
\begin{center}
\includegraphics[scale = 0.65]{newimagepaper.pdf}
%\includegraphics[scale = 0.45]{image_paper222.png}
\caption{\small{Physical arrangements of atom and atom in a cavity. In
    both of these arrangements we consider a source which stimulates
    the atom provoking it to spontaneously emit, once it decays. We
    consider a detector in two directions, and we keep a register of
    the number of photons measured in each direction. (a) In the case
    for the atom we don't expect a correlation between m (the number
    of photons measured in the upper side of the atom) and n (the
    number of photons measured in the right side of the atom); (b) for
    the atom in the cavity (a cavity with some loss rate) we study the
    possibility that the cavity generates a correlation between the
    emissions of the atom and the emissions of the cavity, which
    correspond to the emissions that leak through mirror
    2.}} \label{probdisult}
\end{center}
\end{figure*}
\end{center}

In the case of a two-level atom in free space, the absence of
correlation between different channels is the result of the markovian
approximation, which assumes that the environment has no memory of
previous interactions with the system \cite{daley2014quantum}. Two
atomic emissions would be correlated if one of the emissions stay
registered in the environment and, somehow, influence the second
emission of a two-level atom at a later time; the Markovian
approximation does not allow memory effects and there is no
correlation between the number of emissions of each source: knowing
the number of photons emitted in some region of the space during some
time does not give me any information on the number of photons emitted
in other region of the space. Nevertheless, for the case of an atom
inside a cavity, before a photon leaks the cavity, it will interact
with the atom for some time. This interaction with the atom before the
emission generates a correlation between photons that leak the cavity
through its mirror and photons that leak the cavity through its side.

We use quantum trajectory theory to theoretically calculate the
correlation between different emission channels. A quantum trajectory
is the description of a continuously monitored quantum system
conditioned on a particular past history of coherent evolution and
collapse \cite{Carmichael1993Open}. These trajectories are simulated
through a stochastic process, which define the times when the
collapses occur. Each trajectory gives us the number of photon emitted
in each channel. Simulating a large number of trajectories and
registering the number of photon emissions into the two channels, we
obtain its correlation. The correlation varies with the cavity
linewidth and the atom-cavity coupling. For a very bad cavity we
recover the free space result: there is no correlation between the two
channels.

This article is organized as follows: A general overview of the driven
Jaynes-Cummings model is presented in section \ref{sc:drivenjc}. In
section \ref{sc:distributions} we obtain probability distributions
that relate the number of spontaneous and cavity emissions. In section
\ref{sc:correlation} we calculate the correlation between the two variables.
Concluding remarks are given in section \ref{sc:conclusions}

\section{Driven Jaynes-Cummings model}\label{sc:drivenjc}
We consider a system consisting of a two-level atom, coupled to a mode
of a leaky cavity. The mode is driven by a coherent field resonant
with the atomic transition and the cavity mode.
% In order to account for
% dissipation one may use a non-hermitian Hamiltonian to describe the
% system \cite{bla}. Using this description for the system will turn
% useful at the moment of using quantum trajectory theory. Such
% Hamiltonian can be separated into hermitian and non-hermitian terms.
%\begin{equation}
%H = H_s - \frac{i\hbar}{2}\sum_m C^\dagger_n C_n .
%\end{equation}
The Hamiltonian of this system, in the rotating wave approximation is
given by
\begin{equation}
H_s = H_{at} + H_{cav} + H_{atcav} + H_{lascav}, \label{mainham}  
\end{equation}
where the atom and cavity terms are, respectively
\begin{subequations}
\begin{equation}
H_{at} = \tfrac{1}{2}\hbar \omega \sigma_z,    
\end{equation}
\begin{equation}
H_{cav} = \hbar \omega  a^\dagger a,  
\end{equation}
while the coupling between atom and cavity, and cavity and coherent
field are
\begin{equation}
H_{atcav} = i\hbar g(a\sigma_+ - a^\dagger \sigma_-),    
\end{equation}
\begin{equation}
H_{lascav} = i\hbar \mathcal{E}(ae^{i\omega t} - a^\dagger e^{-i\omega t}),    
\end{equation}
\end{subequations}
where the annihilation operator $a$ of a single photon in the cavity,
and the creation operator $a^\dagger$ obey $[a, a^\dagger] = 1$. The
operators $\sigma_-, \sigma_+$ account for the atomic lowering and
raising operators, respectively, and the operator $\sigma_z$ accounts
for the population difference between the atomic levels. These
operators obey
$[\sigma_+, \sigma_-] = \sigma_z, \ [\sigma_\pm, \sigma_z] = \mp
2\sigma_\pm$. The strength of the coupling between atom and cacity
field is given by the constant
\begin{equation}
g = \sqrt{\frac{\omega d^2}{2\hbar \epsilon_0 V_Q}},
\end{equation}
where $V_Q$ is the mode volume , $d$ is the atomic dipole , and
$\epsilon_0$ is the permitivity of free space. $\mathcal{E}$ is a term
proportional to the coherent field amplitude. Dissipation is
introduced by the following non-hermitian Hamiltonian
\begin{equation} \label{nh}
H_{nh} = H_{dec} + H_{leak},
\end{equation}
where the terms corresponding to spontaneous emission of the atom and cavity losses are
\begin{subequations}
\begin{equation}
H_{dec} = - i\hbar\frac{\gamma}{2}\sigma_+\sigma_-,
\end{equation}
\begin{equation}
H_{leak} = - i\hbar\kappa a^\dagger a\, .
\end{equation}
\end{subequations}
where $\kappa$ and $\gamma$ are the cavity loss and spontaneous decay
rate. The evolution between jumps is given by $H=H_s+H_{nh}$. This
evolution is interrumped by spontaneus emission by the atom or when a
photon leaks the cavity.

We now summarize te quantum trajectory formalism \cite{bla} that we
use to solve the system. We start with a state which represents a
ground state of the atom with no photons in the cavity,
$\ket{\phi(t = 0)} = \ket{\downarrow} \times \ket{0}$, we evolve it
with the Schrödinger equation through some time $\delta t$, using the
non-hermitian Hamiltonian
\begin{equation}
H = H_s +H_{nh}\, .
\end{equation}
Using a non-hermitian Hamiltonian will have as a consequence that the
probability won't be conserved \cite{Sakurai:1167961}. The evolution
of the state through the schrödinger equation will be interrupted by a
quantum jump – an abrupt change on our state in which a photoemission
has ocurred. The probability for such quantum jump to happen will be
given by the collapse probability
\begin{equation} \label{probcol}
\delta p = \sum_n \delta p_n,
\end{equation}
where 
\begin{eqnarray} \label{relprob}
\delta p_1 &=& \gamma \bra{\phi (t)} \sigma_+
               \sigma_-\ket{\psi (t)}\delta t \\
  \delta p_2 &=& 2\kappa \bra{\phi (t)} a^\dagger a\ket{\psi (t)}\delta t 
\end{eqnarray}
We use these collapse probabilities to simulate the quantum
trajectories, where we compare the collapse probability of eq.
\eqref{probcol} with a random number $\epsilon$, uniformly distributed
between zero and one. In the case the condition $\delta p > \epsilon$
is fulfilled we simulate that a quantum jump has happened, by acting
with one of the collapse operators. The operator with which we'll act
on the state will be given according to the relative probabilities of
eq. \eqref{relprob}.
\begin{figure}[!t] 
\centering
\includegraphics[scale = 0.5]{distributioneng.pdf}
\caption{\small{Probability distribution of spontaneous emissions for different number of cavity losses in a driven Jaynes-cummings model, doing $100,000$ quantum trajectory simulations, with parameters $\mathcal{E}  = \kappa = \gamma = g = 1$.}} \label{probdiss}
\end{figure}
Using equation \eqref{probcol} one can easily identify the
corresponding collapse probabilities of the system. Having identified
the collapse operators and the collapse probability, we simulate
quantum trajectories, in which we keep count of the number of quantum
jumps for each collapse operator, relating the number of quantum jumps
associated to spontaneous emissions for each number of quantum jumps
associated to cavity emissions until we reach a maximum number of
cavity emissions, which we establish. The procedure of register of
emissions is summarized in algorithm \ref{alg1}.

@@

\section{Counting photons emitted in different channels}\label{sc:distributions}
In this section we use the quantum trajectory formalism to calculate
the distribution probability of the number of spontaneous emissions by
the atom conditioned to the number of photons that leaked the cavity
from its mirror .
\subsection{Probability distributions of emissions}

@@

\section{Correlation between photons emitted in different channels}\label{sc:correlation}
So far we have obtained estimations for the number of spontaneous emission for each measured number of cavity emissions. From our results it is obvious how the number of spontaneous emissions will increase with respect to the number of cavity emissions, given that more time will pass and more emissions will occur. One can also see how increasing the cavity linewidth $\kappa$ and keeping the other parameters constant will translate into a decrease of spontaneous emissions with respect to the number of cavity emissions. However, one question remains: is there a direct correlation between these two quantities? If yes, how this varies with respect to the cavity linewidth. From the beginning one could expect that in the case for a big $\kappa$ there would be no correlation at all, since this situation will be equivalent to the situation where there is no cavity.

@@

\begin{center}
\begin{figure}[t!]
\begin{center}
\includegraphics[scale = 0.45]{million1.pdf}
\caption{\small{Calculation of correlation using 500 time intervals, fixing $\expval{n} \approx 1$, $\gamma =$ 1.0, $g = $ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}} \label{corrxy}
\end{center}  
\end{figure}
\end{center}

\begin{center}
\begin{figure}[h!]
\begin{center}
\includegraphics[scale = 0.45]{million2.pdf}
\caption{\small{Correlation using different temporal intervals, fixing $\expval{n} \approx 1$, $\gamma =$ 1.0, $g =$ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}}  \label{errorzz}
\end{center}
\end{figure}
\end{center}
%kncrease or increases
From Fig. \ref{corrxy} we see that, as we expected, the correlation goes to zero as we increase the cavity linewidth. Nonetheless, perhaps a more interesting question is: how high can this correlation be? Trying with values for $\kappa/\gamma$ lower than $0.1$, we notice that the correlation's increase stops and a decrease begins. It is possible that this stop in the increase of the correlation is due to the fact that if we keep decreasing the cavity linewidth it will come a point where the number of emissions will decrease considerably, diminishing the correlation. If this is the case we should expect that as we increase the temporal intervals, %the cavity linewidth at which the correlation starts decreasing should be smaller.
we also see an increment of the correlation.

@@

\section{Conclusions}\label{sc:conclusions}
In this work we considered a driven Jaynes-Cummings system. We made a program in which, through the use of quantum trajectory theory, we were able to obtain probability distributions that relate the number of spontaneous emissions given certain number of cavity emissions. Through the probability distributions we obtained estimations for the number of spontaneous emissions by measuring cavity emissions, considering the correspondent error. Finally we study the existing correlation where we saw how this correlation decreases as we increase the cavity linewidth. However, if we try with values for  $\kappa/\gamma < 0.1$, there comes a point where the increase stops and we see a decrease. We believe this is related to the fact that if we use enough small values of $\kappa$ there will come a point where the emission of photons will be too low and this will imply a decrease in the correlation. The results in this work provide a tool that could be useful in the manipulation of single photons product of spontaneous emission, and provide insight into the physical behavior of the driven Jaynes-Cummings model.

@@

Support by UNAM, projects CONACyT and UNAM PAPIIT IG100518.
